(Automatic) Speech Recognition Project --- Attacks on Neural Networks in a Lightweight Speech Pseudonymization Pipeline

### 2024-06-06 paper/paper.tex
Fixed that unholy grad bug I am euphoric

\subsection{Evasion Attacks}
We attack an ASV model that has been fine-tuned on the clean test set used for the backdoor attack.
We attack this model with both an FGSM \citep{goodfellow2015explaining} and a PGD \citep{madry2018towards} attack.
For our experiment, we will use $\epsilon = \frac{8}{255}$ for the FGSM model, and $\epsilon = \frac{8}{255}$ and $\alpha = \frac{2}{255}$ for the PGD model.
We run the PGD model for 10 steps.
The implementation of the FGSM and PGD attacks is taken from the Torchattacks \citep{kim2020torchattacks} library and is refactored to fit our data.

We use the evasion attacks to generate perturbed utterances with the speaker with ID 0 as the target.
The perturbations should then move any audio file closer to the space of speaker ID 0 utterances.
We feed these perturbed inputs to the ASV model, and measure its Speaker Identification Accuracy and Attack Success Rate.
We also measure the clean ASR model's Word Error Rate on these perturbed inputs.

\section{Results}
\subsection{Backdoor Attacks}
\begin{figure*}
    \centering
    \includegraphics[width=0.9\textwidth]{backdoor_metrics.png}
    \caption{An overview of the measured metrics for the JingleBack attack. Per poisoning rate, the Word Error Rate (WER), Word Error Rate Increase (WERI), Speaker Identification Accuracy (Acc), Attack Success Rate (ASR), and Clean Accuracy Drop (CAD) are given.}
    \label{fig:backdoor_metrics}
\end{figure*}

>>>>

\subsection{Evasion Attacks}
We attack an ASV model that has been fine-tuned on the clean test set used for the backdoor attack.
We attack this model with both an FGSM \citep{goodfellow2015explaining} and a PGD \citep{madry2018towards} attack.
For our experiment, we will use $\epsilon = \frac{8}{255}$ for the FGSM model, and $\epsilon = \frac{8}{255}$ and $\alpha = \frac{2}{255}$ for the PGD model.
We run the PGD model for 10 steps.
The implementation of the FGSM and PGD attacks is taken from the Torchattacks \citep{kim2020torchattacks} library and is refactored to better fit our needs.

We use the evasion attacks to generate perturbed utterances with the speaker with ID 0 as the target.
This means that the perturbations caused by the attack should move any utterance closer to the space of utterances by the speaker with ID 0.
We feed these perturbed inputs into the ASV model, and measure its Speaker Identification Accuracy and Attack Success Rate.
We also measure the clean ASR model's WER on these perturbed inputs.

\section{Results}
The backdoored and perturbed utterances computed during the execution of the experiments have been saved as audio files.
Examples of clean, JingleBack backdoored, FGSM perturbed, and PGD perturbed audio can be found at the following URL: \url{https://github.com/daanbrugmans/ru-automatic-speech-recognition-23-24/tree/main/audio}

\subsection{Backdoor Attacks}
\begin{figure*}
    \centering
    \includegraphics[width=0.9\textwidth]{backdoor_metrics.png}
    \caption{An overview of the measured metrics for the JingleBack attack. Per poisoning rate, the Word Error Rate (WER), Word Error Rate Increase (WERI), Speaker Identification Accuracy (Acc), Attack Success Rate (ASR), and Clean Accuracy Drop (CAD) are given.}
    \label{fig:backdoor_metrics}
\end{figure*}
